Draft1

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Adding regression tables, etc.

The interaction term $\beta_5FearFailure*PerceivedOpportunities$ was added to the regression because the survey question regarding "Fear of Failure" was only proposed to survey respondents who indicated they do perceive opportunities

>>>>

The interaction term $\beta_5FearFailure*PerceivedOpportunities$ was added to the regression because the survey question regarding "Fear of Failure" was only proposed to survey respondents who indicated they do perceive opportunities to start a business.

```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}

# Import df of dependent and independent variables
CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")

# Run linear regression R1
R1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)

# Run linear regression R2
R2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)

# Run linear regression R3
R3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}

# Library Stargazer for regression output tables
library(stargazer)

# Create regression output table
labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')

dlables <- c('National Level Average Percent Entrepreneurial Intention', 'National Level Nascent Entrepreneural Activity', 'National Level Average Percent Owning a Business')

stargazer::stargazer(R1, R2, R3, covariate.labels = labels, dep.var.labels = dlables,
                     title = 'Linear Regression Estimates', digits = 2, type = 'html')
